Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-08 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:08	19:05:54	(Tue 8.Sep)

\Fig{oversampling_mosaic_bounds_beta} illustrates which $\beta$-value LCA prefers for different regions in the image of the cross. Red marker lines are used to pinpoint the cut line and location of the anchor. Observe that in the anchor region only rectangular windows are used, which is the reason for the anchor resolution being measured to the same value regardless of the upper bound of $\beta$ in \Fig{oversampling_mosaic_bounds}.

Unlike the method described by Synnev\aa{}g~\cite{Synnevag2008} we do not let LCA choose from  inverted Kaiser windows. These have a spatial response with mainlobe width narrower than that of a rectangular window, but at the expense of drastically increased white noise gain. We have found that these windows hardly ever get used on experimental data, in particular steered versions which ever worsened white noise gain. We can infer the same from \Fig{mvdr_selected_windows} by noting that the maximum sidelobe level rarely exceeds the rectangular window level of -13\;dB.

@@

What is the best set of Kaiser windows to use with LCA, and how much should they be steered? To investigate this we constructed large and equally sized window databases containing windows with varied upper boundaries for $\beta$ and $\phi$. As lower boundaries we chose $\beta=0$ and $\phi=0^\circ$, which includes the rectangularly weighted DAS image. The images produced are shown in \Fig{oversampling_mosaic_bounds}. The lateral distance $\Delta x$ between the -3dB points of the anchor is measured for each image, with the reference $\Delta x_\text{ref}$ being the rectangularly weighted DAS image. This measure is also called the full width half maximum (FWHM). In the case of a imaging a point scatter, it is closely related to the resolution of of the system. For a rectangular window, for instance, the resolution is 0.89$\cdot$FWHM.

The images show much improved sidelobe suppression with a an upper for bound for $\beta$ of 2, but it improved further as this bound was adjusted up to 5. After 5 no noticeable difference was observed. The images also demonstrate that increasing the steering $\phi$ improves the resolution of the strong scatterers. For this sonar the Rayleigh resolution 0.72$^\circ$, or roughly 24\,cm at the imaging range of 19\,m. we suggest to steer either to 50\% or 100\% of the -3dB width, which leads to a resolution of 73\% or 54\% of the rectangular window, respectively. As lower boundaries we choose $\beta=0$ to always include a rectangular window, and $\phi=0$ to always include the centered window.

LCA images created with a large and equal size window database, but where the upper bounds for $\beta$ and $\phi$ is varied. The upper left image is equal to DAS with a rectangular window. For all images we measure the lateral distance $\Delta x$ between the two -3dB points of the anchor. These are specified relatively to the reference distance  $\Delta x_\text{ref}$ from the upper left DAS image.

@@

>>>>

\Fig{oversampling_mosaic_bounds_beta} and \Fig{oversampling_mosaic_bounds_phi} illustrates which $\beta$ and $\phi$ values LCA prefers for different regions in the image of the cross. Red marker lines are used to pinpoint the cut line, location of the anchor and strong scatter points on the cross. Observe that in the anchor region only narrow responses ($\beta=0$) are used, which is the reason for the anchor FWHM being measured to the same value regardless of the upper bound of $\beta$ in \Fig{oversampling_mosaic_bounds}. On other scatterers with strong nearby lateral interference LCA prefers wider windows to suppress the interference. When allowed LCA always choose windows steered away from the sources, and should not be allowed to select windows that are steered more than the 3\,dB width of the window. We observed image oscillations when exceeding this bound.

Unlike the method described by Synnev\aa{}g~\cite{Synnevag2008} we do not let LCA choose from  inverted Kaiser windows. These have a spatial response with mainlobe width narrower than that of a rectangular window, but at the expense of drastically increased white noise gain. We have found that these windows hardly ever get used on experimental data, in particular steered versions with an even worse white noise gain. We can infer the same from \Fig{mvdr_selected_windows} by noting that the maximum sidelobe level rarely exceeds the rectangular window level of -13\;dB.

@@

What is the best set of Kaiser windows to use with LCA, and how much should they be steered? To investigate this we constructed large and equally sized window databases containing windows with varied upper boundaries for $\beta$ and $\phi$. As lower boundaries we chose $\beta=0$ and $\phi=0^\circ$, which includes the symmetric rectangularly weighted DAS image. The images produced are shown in \Fig{oversampling_mosaic_bounds}. In each image we computed the lateral distance $\Delta x$ between the -3dB points of the anchor, with the reference $\Delta x_\text{ref}$ being the rectangularly weighted DAS image. A forth order polynomial fit was used in this computation. This measure is also called the full width half maximum (FWHM). In the case of a imaging a point scatter, it is closely related to the resolution of of the system. For a rectangular window, for instance, the system resolution is $\Delta = \text{FWHM}/0.89$~\cite{Harris1978}.

The images in \Fig{oversampling_mosaic_bounds} much improved sidelobe suppression with a an upper for bound for $\beta$ of 2, but it improved further as this bound was adjusted up to 5. No noticeable difference were observed for higher values than 5. The images also demonstrate that increasing the steering $\phi$ improves the resolution of the strong scatterers. For this sonar the Rayleigh resolution is $\Delta=0.0125$ radians (0.72$^\circ$), thus a point scatterer imaged at 19\,m with a rectangular DAS would have a lateral FWHM of $0.125\cdot19\,\text{m}\cdot0.89=21\,\text{cm}$. This is close to the FWHM of the anchor in the DAS image in \Fig{oversampling_mosaic_bounds}. As we increase steering to either 50\% or 100\% of the -3dB width, the FWHM drops to 73\% or 53\% to that of the rectangular window, respectively.

@@

TODO
